An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-11-26 EconGrowth2.Rnw
Added commented lines for creating the CES Spaghetti graphs from archive data.

>>>>

The resample model predictions for each nesting 
in Figure~\ref{fig:CES_GDP_Lattice_Graph} can be shown as gray lines 
beneath superimposed on the historical data as shown
in Figures~\ref{fig:CES_Spaghetti_Graph_kl}--\ref{fig:CES_Spaghetti_Graph_ekl}. 
Figure~\ref{fig:CES_Spaghetti_Graph_kl} shows CES model resample predictions
for the ($kl$) nesting (without energy).

<<CES_Spaghetti_Graph_kl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Indexed GDP predictions for 1000 CES resample models for the ($kl$) nesting (without energy). **** Need to change the order of the countries to correspond to countryAbbrevsForGraph. Need to plot historical data as open circles instead of red lines. ****">>=
# createCESSpaghettiGraph(energyType=NA, archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
# createCESSpaghettiGraph(energyType=NA, archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
createCESSpaghettiGraph(energyType=NA)
@

Figure~\ref{fig:CES_Spaghetti_Graph_kle} shows CES model 
resample predictions for the ($kl$)$e$ nesting.

<<CES_Spaghetti_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Indexed GDP predictions for 1000 CES resample models for the ($kl$)$e$ nesting (with energy). Only 50 resample models are shown. **** Need to change the order of the countries to correspond to countryAbbrevsForGraph. Need to plot historical data as open circles instead of red lines. ****">>=
# createCESSpaghettiGraph(energyType="Q", nest="(kl)e", archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
# createCESSpaghettiGraph(energyType="Q", nest="(kl)e", archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
createCESSpaghettiGraph(energyType="Q", nest="(kl)e")
@

<<CES_Spaghetti_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Indexed GDP predictions for 1000 CES resample models for the ($le$)$k$ nesting (with energy). **** Need to change the order of the countries to correspond to countryAbbrevsForGraph. Need to plot historical data as open circles instead of red lines. ****">>=
# createCESSpaghettiGraph(energyType="Q", nest="(le)k", archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
# createCESSpaghettiGraph(energyType="Q", nest="(le)k", archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
createCESSpaghettiGraph(energyType="Q", nest="(le)k")
@

<<CES_Spaghetti_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Indexed GDP predictions for 1000 CES resample models for the ($ek$)$l$ nesting (with energy). **** Need to change the order of the countries to correspond to countryAbbrevsForGraph. Need to plot historical data as open circles instead of red lines. ****">>=
# createCESSpaghettiGraph(energyType="Q", nest="(ek)Le", archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
# createCESSpaghettiGraph(energyType="Q", nest="(ek)l", archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
createCESSpaghettiGraph(energyType="Q", nest="(ek)l")
@
